\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}

I would like to thank my advisor, Dr. Ivan V. Bajić, for his guidance and support throughout my graduate studies.
His feedback in reviewing and editing my papers and thesis was invaluable, as was his advice on research and career development.
He first supervised my undergraduate Bachelor's thesis, during which his encouragement motivated me to develop a prototype for demonstration at the NeurIPS 2019 conference.
His insight in the subject areas of compression, information theory, and deep learning helped guide me in my research.

I would also like to thank my committee members, including:
Dr. Mirza Faisal Beg, who was my supervisor for an NSERC Undergraduate Student Research Awards (USRA) research project, and provided me with an opportunity to work on a challenging problem in computer vision, related to medical mobile applications;
Dr. Jie Liang, who first inspired and intrigued me with his lectures on Multimedia Communications Engineering involving the subjects of compression and deep learning;
and Dr. Andrew Rawicz, who taught our Capstone project course during my undergraduate studies, instilling within us the value of a practical approach to engineering, as well as skills for managing technical projects.

I also greatly enjoyed my time as an intern at Interdigital's AI Lab headed by Dr. Jaideep Chandrashekar.
My discussions with Dr. Fabien Racapé and Dr. Hyomin Choi significantly improved my understanding of this field.
I also enjoyed my discussions with other interns, namely Ujwal Dinesha and Ezgi Özyılkan, who imparted upon me a greater appreciation for reinforcement learning and information theory, respectively.
% There, I worked on a variety of projects in learned image compression.
% CompressAI Trainer.

I would also like to show my appreciation for the community at SFU, including my friends and peers, as well as the professors of the schools of engineering science and computer science, and the departments of physics and mathematics.
Within the SFU Multimedia Lab research group, I would also mention Alon Harell and Anderson de Andrade for their interest in my work as well as discussions within the subject area.

And of course, for the never-ending support from my family, including my mother and sister, I am grateful.


% Ivan V. Bajić
% Mirza Faisal Beg
% Jie Liang
% Andrew Rawicz
%
% Hyomin Choi
% Fabien Racapé
% Ujwal Dinesha
% Ezgi Özyılkan
%
% Alon Harell
% Anderson de Andrade
%
% Family, friends
% My mother and sister

